How cryptic is cryptic diversity? \newline Machine learning approaches to fine scale variation in the morphology of \textit{Emys marmorata}.

### 2013-06-17 documents/turtle_presentation.Rnw
fixing up various figures to make them more readable

\section{Introduction}
\begin{frame}
  \frametitle{Cryptic diversity}
  % image of example taxa that are morphologically identical and are only differentiated via genetic means
  %
  Crytic species are species delimitated via molecular means which were not/cannot be identified via morphology.

@@

\section{Methods}
\begin{frame}
  \frametitle{Methods: morphometrics}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
        %\item \Sexpr{nrow(turtle.adult)} adult individuals
        \item plastral (``belly'') shape
        \item landmarks averaged across bilat axis
        \item total 13 landmarks, 7 on bilat axis, 6 off
        \item geographic information known/inferred
      \end{itemize}
    \end{column}
    \begin{column}{0.5\textwidth}
      \begin{figure}[h]
        \centering
        \captionsetup{justification = raggedleft, slc = off}
        \includegraphics[width = \textwidth, keepaspectratio = true]{figure/plastra}
        \caption*{\scriptsize{Angielczyk \textit{et al.} 2011 \textit{Evolution}}}
        \label{fig:plast}
      \end{figure}
    \end{column}
  \end{columns}
\end{frame}

@@

@@

<<fig.width = 3.75, fig.height = 3.75>>=
# get mean of each class
spi <- turtle.adult$spinks
wspi <- lapply(levels(spi), function(x, y) which(y == x), y = spi)
mspi <- lapply(wspi, function(x, y) mshape(y[, , x]), y = turtle.land.adult)
par(mfrow = c(2, 2), mar = c(0, 0, 1, 1) + 0.1, oma = c(5, 4, 0, 0) + 0.1,
    xaxt = 'n', yaxt = 'n')
mapply(function(x, m, n) {
      tpsgrid(x, m, mag = 2)
      title(main = paste(n))}, x = mspi, n = levels(spi),
      MoreArgs = list(m = mt), SIMPLIFY = FALSE)
par(mfrow = c(1, 1))
@

@@

par(mfrow = c(1, 2), mar = c(0, 0, 1, 1) + 0.1, oma = c(5, 4, 0, 0) + 0.1,
    xaxt = 'n', yaxt = 'n')
tpsgrid(turtle.land.adult[, , fst.min], mt, mag = 2)
title(main = 'min observed')
tpsgrid(turtle.land.adult[, , fst.max], mt, mag = 2)
title(main = 'max observed')
par(mfrow = c(1, 1))
@

@@

\begin{frame}
  \frametitle{Shape across PC8}
<<fig.width = 5>>=
par(mfrow = c(1, 2), mar = c(0, 0, 1, 1) + 0.1, oma = c(5, 4, 0, 0) + 0.1,
    xaxt = 'n', yaxt = 'n')
tpsgrid(turtle.land.adult[, , snd.min], mt, mag = 2)
title(main = 'min observed')
tpsgrid(turtle.land.adult[, , snd.max], mt, mag = 2)
title(main = 'max observed')
par(mfrow = c(1, 1))
@
\end{frame}

>>>>

\section{Introduction}
\begin{frame}
  \frametitle{Cryptic diversity}
  % image of example taxa that are morphologically identical and are only differentiated via genetic means
  %
  Crytic species are species delimitated via molecular means. Taxa were not/cannot be identified via morphology.

@@

\section{Methods}
\begin{frame}
  \frametitle{Methods: morphometrics}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
        \item \Sexpr{nrow(turtle.adult)} adult individuals
        \item plastral (``belly'') shape
        \item landmarks averaged across bilat axis
        \item total 13 landmarks, 7 on bilat axis, 6 off
        \item geographic information known/inferred
      \end{itemize}
    \end{column}
    \begin{column}{0.5\textwidth}
      \begin{figure}[h]
        \centering
        \captionsetup{justification = raggedleft, slc = off}
        \includegraphics[width = \textwidth, keepaspectratio = true]{figure/plastra}
        \caption*{\scriptsize{Angielczyk \textit{et al.} 2011 \textit{Evolution}}}
        \label{fig:plast}
      \end{figure}
    \end{column}
  \end{columns}
\end{frame}

@@

  Analogous to \textit{k}-means clustering, a divisive clustering algorithm.

@@

<<fig.width = 3.75, fig.height = 3.75>>=
# get mean of each class
spi <- turtle.adult$spinks
wspi <- lapply(levels(spi), function(x, y) which(y == x), y = spi)
mspi <- lapply(wspi, function(x, y) mshape(y[, , x]), y = turtle.land.adult)
par(mfrow = c(2, 2), mar = c(0, 0, 1, 1) + 0.1, oma = c(5, 4, 0, 0) + 0.1,
    xaxt = 'n', yaxt = 'n')
mins <- lapply(mspi, function(x) min(x[, 2]))
mins <- min(unlist(mins))
mapply(function(x, m, n) {
      #tpsgrid(x, m, mag = 2, ext = 0, cex = 2)
      plotRefToTarget(M1 = m, M2 = x, mag = 2)
      title(main = paste(n))}, x = mspi, n = levels(spi),
      MoreArgs = list(m = mt), SIMPLIFY = FALSE)
par(mfrow = c(1, 1))
@

@@

par(mfrow = c(1, 2), mar = c(0, 0, 1, 1) + 0.1, oma = c(5, 4, 0, 0) + 0.1,
    xaxt = 'n', yaxt = 'n')
tpsgrid(turtle.land.adult[, , fst.min], mt, mag = 2)
#plotRefToTarget(M1 = mt, M2 = turtle.land.adult[, , fst.min])
title(main = 'min observed')
tpsgrid(turtle.land.adult[, , fst.max], mt, mag = 2)
#plotRefToTarget(M1 = mt, M2 = turtle.land.adult[, , fst.max])
title(main = 'max observed')
par(mfrow = c(1, 1))
@

@@

\begin{frame}
  \frametitle{Shape across PC8}
<<fig.width = 5>>=
par(mfrow = c(1, 2), mar = c(0, 0, 1, 1) + 0.1, oma = c(5, 4, 0, 0) + 0.1,
    xaxt = 'n', yaxt = 'n')
tpsgrid(turtle.land.adult[, , snd.min], mt, mag = 2)
#plotRefToTarget(M1 = mt, M2 = turtle.land.adult[, , snd.min])
title(main = 'min observed')
tpsgrid(turtle.land.adult[, , snd.max], mt, mag = 2)
#plotRefToTarget(M1 = mt, M2 = turtle.land.adult[, , snd.max])
title(main = 'max observed')
par(mfrow = c(1, 1))
@
\end{frame}
